\documentclass[12pt]{article}
\setlength{\parindent}{0in}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\begin{document}
\begin{titlepage}
This is a title page
\end{titlepage}
\newpage
This is a test for citations.\textsuperscript{1}
\newpage
This is a test for CSE Citations, I think they need to be at the END of a sentence.\textsuperscript{2}
\newpage
\begin{multicols} {2} [REFERENCES]
(1) White PJ, Proffitt KM, Mech LD, et al. Migration of northern Yellowstone elk: implications of spatial structuring. Journal of Mamm. 2010;91(4):827–837.\newline\newline
(2) Genkai-Kato M, Nozaki K, Mitsuhashi H, Kohmatsu Y, et al. Push-up response of stonefly larvae in low-oxygen conditions: Push-up response of stonefly larvae. Eco. research. 2000;15(2):175–179.\newline\newline
(3) Teasdale, T., Trying to see if this works. Journal of Coding during COVID. 2020:91(4)678-987.\newline \newline
(4) Genkai-Kato M, Nozaki K, Mitsuhashi H, Kohmatsu Y, et al. Push-up response of stonefly larvae in low-oxygen conditions: Push-up response of stonefly larvae. Eco. research. 2000;15(2):175–179.\newline\newline
(5) Genkai-Kato M, Nozaki K, Mitsuhashi H, Kohmatsu Y, et al. Push-up response of stonefly larvae in low-oxygen conditions: Push-up response of stonefly larvae. Eco. research. 2000;15(2):175–179.\newline\newline
(6) Genkai-Kato M, Nozaki K, Mitsuhashi H, Kohmatsu Y, et al. Push-up response of stonefly larvae in low-oxygen conditions: Push-up response of stonefly larvae. Eco. research. 2000;15(2):175–179.\newline\newline
(7) Teasdale, T., Trying to see if this works. Journal of Coding during COVID. 2020:91(4)678-987.\newline \newline
(8)Teasdale, T., Trying to see if this works. Journal of Coding during COVID. 2020:91(4)678-987.\newline \newline 
\end{multicols}
\end{document}